Thread Pool in GeckoDB/BOLSTER

### 2018-06-13 Presentations/Milestone3/presentation.tex
added slide "optimization opportunities" for milestone 3

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone III: Implementation \& evaluation setup}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise, Benedikt Zeilinger}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

@@

@@

\begin{frame}
	\begin{itemize}
		\item Introduction and Preliminaries mostly completed
		\item Implementation described, including our used concepts and basic ideas how to build and operate the pool
		\item Still required is the Evaluation(since we still need to perform it), the description of our testing environment and our final conclusion
	\end{itemize}
\end{frame}

>>>>

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone III: Implementation \& evaluation setup}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

@@

\begin{frame}
	\frametitle{Possible Optimization Opportunities}
	\begin{itemize}
		\item Improve Priority Queue data structure
		\item Change distribution of Wait-Slots
		\item Reduce number of dynamic allocations
		\item Adjust number of threads to increase occupancy
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\begin{itemize}
		\item Introduction and Preliminaries completed
		\item Implementation described, including our used concepts and basic ideas how to build and operate the pool
		\item Still required are the evaluation (since we still need to
			measure the actual performance), the description of our testing environment and our final conclusion
	\end{itemize}
\end{frame}
